### 2018-01-31 CO749-GraphColoring/assignments/A2.tex
finished A2

	TODO

>>>>

	Suppose not. Then there exists an edge $uv \in E(G)$ such that $L(u) \neq L(v)$. From Claim $3.4$ we may assume $L(u) \subset L(v)$. Since $|L(u)|$ and $|L(v)|$ are even, this implies there exist distinct colors $c, c' \in L(v)\backslash L(u)$. Since $c, c' \not\in L(u)$, $G(c)$ and $G(c')$ have common endpoint $v$. Thus we may assume $G(c) \subseteq G(c')$. So $P = G(c) \cap G(c') = G(c)$ has an end point in common with $G(c)$ and the other endpoint, $v$, in common with $G(c')$.
	By Claim $3.3$, $|V(P)|$ is even, but then the existence of $P$ contradicts Claim $3.2$.
